---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# statstring

<!-- badges: start -->
<!-- badges: end -->

The goal of statstring is to facilitate formatting outputs of statistical tests when they're pasted into R markdown files in APA style. Currently, statstring can format results of ANOVA outputs generated by `stats::aov()`, `summary(stats::aov)`, `rstatix::get_anova_table()`, and `apaTables::apa.aov.table()`. To format the outputs for R markdown, simply pass one of the previously listed ANVOA objects to the function `format_anova_string()`.

The package can also handle outputs from an independent samples _t_-test, generated by `stats::t.test()`. The formatted output includes the mean difference and a 95% confidence interval (CI) on the mean difference.

You can also use the package to extract and format _R_^2^ for a model produced by `stats::lm()` or `summary(stats::lm())` using the function `format_r2()`. 

Finally, you can use this package to format point estimates and 95% CI around the point estimate using `format_confint()`.

## Installation

You can install the released version of statstring from Github with: `devtools::install_github("silverer/statstring")`


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(statstring)
data("warpbreaks")
#Results of a t-test
t.res = stats::t.test(breaks~wool, data = warpbreaks, var.equal=T)
t.res
t.str = format_tstat_apa(t.res)
#Results of ANOVA
aov.res = stats::aov(breaks~wool*tension, data = warpbreaks)
summary(aov.res)
aov.intrxn = format_anova_string(aov.res)
#Using a specific predictor
aov.wool = format_anova_string(summary(aov.res), predictor = "wool")
#Getting all F-statistics
all.aov.results = format_anova_string(summary(aov.res), get.all=T)

#Results of linear model
lm.res = stats::lm(breaks~ wool + tension, data = warpbreaks)
summary(lm.res)
r2 = format_r2(lm.res)
```

For the t-test, the output looks like `r t.str`. 

For the ANOVA, the output corresponds to the last factor in the model (in this case, the interaction term): `r aov.intrxn`. You can also specify which predictor you want to extract, for example, the term for wool is: `r aov.wool`. 

For a linear model using breaks as the criterion and wool and tension as predictors, `r r2`

