---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# statstring

<!-- badges: start -->
<!-- badges: end -->

The goal of statstring is to facilitate formatting outputs of statistical tests when they're pasted into R markdown files in APA style. Currently, statstring can format results of ANOVA outputs generated by `stats::aov()`, `summary(stats::aov)`, `rstatix::get_anova_table()`, and `apaTables::apa.aov.table()`. To format the outputs for R markdown, simply pass one of the previously listed ANVOA objects to the function `format_anova_string()`.

The package can also handle outputs from an independent samples _t_-test, generated by `stats::t.test()`. The formatted output includes the mean difference and a 95% confidence interval (CI) on the mean difference.

You can also use the package to extract and format _R_^2^ for a model produced by `stats::lm()` or `summary(stats::lm())` using the function `format_r2()`. 

Finally, you can use this package to format point estimates and 95% CI around the point estimate using `format_confint()`.

## Installation

You can install the released version of statstring from Github with: `devtools::install_github("silverer/statstring")`


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(statstring)
data("warpbreaks")
#Results of a t-test
t.res = stats::t.test(breaks~wool, data = warpbreaks, var.equal=T)
t.res
t.str = format_tstat_apa(t.res)
#Results of ANOVA
aov.res = stats::aov(breaks~wool*tension, data = warpbreaks)
summary(aov.res)
#Getting all F-statistics
all.aov.results = format_anova_string(summary(aov.res))

#Results of linear model
lm.res = stats::lm(breaks~ wool + tension, data = warpbreaks)
summary(lm.res)
r2 = format_r2(lm.res)
```

For the t-test, the output looks like `r t.str`. 

For ANOVAs, the output corresponds to the order in which terms were entered into the model. For example, the term for wool (the first factor in the model) is: `r all.aov.results[1]`, for tension is `r all.aov.results[2]`, and for the interaction between tension and wool: `r all.aov.results[3]`

For a linear model using breaks as the criterion and wool and tension as predictors, `r r2`

You can also get formatted text outputs that do not include the special characters used for formatting things in markdown, such as the underscore for italics. To turn off markdown formatting, pass the argument `as.markdown=F` to your function.
