---
title: "Introduction"
output: rmarkdown::html_vignette
author: "Elisabeth R. Silver"
date: "07/09/2021"
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}

library(statstring)
```


### Using statstring to format ANOVA outputs

statstring is a package to facilitate formatting ANOVA outputs in APA style.

You can pass a summary object to the `format_anova_string()` function to extract and format an ANOVA result. 

For instance, using the stats::aov() function:


```{r}
data("warpbreaks")
res <- summary(stats::aov(breaks~wool*tension, data = warpbreaks))
str_out <- format_anova_string(res)
```


There was a significant interaction between tension and wool on breaks, `r str_out`.

Using rstatix::get_anova_table() function:


```{r}

res <- rstatix::get_anova_table(rstatix::anova_test(breaks~wool*tension, 
                                                    data = warpbreaks, type = 3,
                                                    effect.size = "pes"))
str_out <- format_anova_string(res)

```


There was a significant interaction between tension and wool on breaks, `r str_out`.


Using apaTables::apa.aov.table() function (also specifying a particular independent variable):


```{r}

res <- apaTables::apa.aov.table(lm(breaks~wool*tension, data = warpbreaks), type = 3)
interaction_out <- format_anova_string(res)

wool_out <- format_anova_string(res, predictor = "wool") #Specify the name of the predictor
tension_out <- format_anova_string(res, predictor = 3) #Can also specify the row of the predictor
```


There was a significant interaction between tension and wool on breaks, `r interaction_out`. There was a main effect of wool on breaks, `r wool_out`. There was a main effect of tension on breaks, `r tension_out`.


### Using statstring to format t-test outputs

You can use statstring to format t-test results as well.

```{r}

indep_test <- stats::t.test(warpbreaks$breaks~warpbreaks$wool)
indep_str <- format_tstat_apa(indep_test)

onesample_test <- stats::t.test(warpbreaks$breaks)
onesample_str <- format_tstat_apa(onesample_test)

```

There was not a significant difference in breaks by wool type, `r indep_str`. The number of breaks differed from zero, `r onesample_str`.

You can also use the outputs of a pairwise comparison directly when formatting a t-statistic

```{r}
mod <- lm(breaks~wool*tension, warpbreaks)
marginal_means <- emmeans::emmeans(mod, c("wool", "tension"))
pairwise_comps <- data.frame(pairs(marginal_means, adjust="tukey"))
cis <- data.frame(confint(pairs(marginal_means, adjust="tukey")))
cis <- cis[,c("contrast", "lower.CL", "upper.CL")]
pairwise_comps <- dplyr::left_join(pairwise_comps, cis, by = "contrast")

pairwise_comps["stat_string"] <- mapply(format_pairwise_comparison,
                                        t_stat = pairwise_comps$t.ratio,
                                        df = pairwise_comps$df,
                                        p_val= pairwise_comps$p.value,
                                        mdiff = pairwise_comps$estimate,
                                        lci=pairwise_comps$lower.CL,
                                        uci = pairwise_comps$upper.CL)
```

Example output: `r pairwise_comps$stat_string[1]`

